Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-16 paper/paper.tex
pass on methodology

\subsection{Clusterization}

@@

This section reports the results obtained by fuzzing inputs, running
those inputs on different engines, and checking the outcomes with a
differential oracle (see Figure~\ref{fig:workflow}).

\subsubsection{Methodology}
In the following, we describe the methodology we used to assess the
impact of cross-engine differential testing in finding bugs on \js{}
engines. To avoid experimental noise, we did \emph{not} fuzz test
files that failed in some engine as per results reported in
Sections~\ref{sec:stability} and~\ref{sec:transplantation}. The
intuition is that we want to make sure that the bug was not
coincidental, \ie{}, the scenario where fuzzing produces an
fault-revealing input based on a test that was already
fault-revealing. That decision ensures that we can establish
cause-effect relationship between fuzzing and the observation of
discrepancy. For that reason, we discarded a total of \Fix{???} test
files from a total of \totalTestFiles{}.Recall that our tool outputs a
set of buckets, that each bucket includes a set of warnings, that each
warning is related to one file, and that a bucket is of ``lo'' or
``hi'' importance, according to the heuristic we
defined. Figure~\ref{fig:distribution} shows the distribution of
number of warnings reported per bucket. We use the names of the
fuzzing tools to refer to the results obtained with those tools. We
inspected each and every bucket for bugs, but observe that the number
of files per bucket is very high in some cases. As such, it would be
impractical to manually inspect all the files in the bucket. For that
reason, we only inspected one file per bucket. For the cases we found
the warning suspicious, we analyzed the parts of the documentation
related to the problem and, if still suspicious, we looked on the bug
tracker of the affected engine for potential duplicates. If none was
reported, we filed a bug report including the test input that
manifested the potential problem and explaining the reasons we were
suspicious. In some cases, we used the Mozilla lithium
tool~\cite{lithium} to minimize the test case. For the cases of false
positives, we identified the source of false positive and moved to the
next bucket.

\begin{figure}[t]
  \centering
  \includegraphics[trim=0 0 0 0,clip,width=0.40\textwidth]{R/histograms/histograms.pdf}  
  \caption{\label{fig:distribution}Distribution of lo and hi warnings
   in buckets.}
\end{figure}

@@

\begin{table*}[h!]
  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued as result of cross-engine
    differential testing.}
  \label{tab:bugs}
  \begin{tabular}{ccccccccc}
    \toprule
    Issue\#    & Date & Fuzz & Engine  & Status  &
    \multicolumn{1}{c}{Url}  & Severity & Priority & Suite \\
    \midrule    
    1  & 4/12 & radamsa & \chakra{}   & \textbf{Fixed}  &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/4978}{\#4978}}
    & 2 & LO & \jsc{} \\ 
    2  & 4/12 & radamsa & \chakra{}   & Rejected  &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/4979}{\#4979}}
    & - & HI & \jsc{} \\
    3  & 4/14 & radamsa & JavascriptCore  & New &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}
    } & -  & HI & \jsc{}    \\
    4  & 4/25 & radamsa & \chakra{}  & \textbf{Fixed}     &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5038}{\#5038}}
    & 2 & HI & \jerry{}   \\
    5  & 4/29 & radamsa & JavascriptCore  & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}
    } & 2  & HI  & \jerry{}\\
    \midrule
    \multirow{2}{*}{6} & \multirow{2}{*}{4/30}  &
    \multirow{2}{*}{radamsa} & \chakra{} & \textbf{Confirmed} &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5076}{\#5076}}
    & 2 & \multirow{2}{*}{HI} & \multirow{2}{*}{TinyJS}\\    
                        &                        &        &
    JavascriptCore & New &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}}
    & - &  & \\
    \midrule
    7 & 5/02 & radamsa & JavascriptCore  & \textbf{Fixed} &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}}
    & 2 & LO & \smonkey{} \\
    8 & 5/10 & radamsa & \chakra{} & \textbf{Confirmed} &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5128}{\#5128}}
    & 3 & HI & \jerry{} \\
    9 & 5/17 & radamsa & \chakra{} & \textbf{Fixed} &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5182}{\#5182}}
    & 2 & HI & \veight{}\\
    10 & 5/24 & radamsa & JavascriptCore & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943}}
    & 2 & HI & \jsc{}\\
    11 & 6/26 & radamsa & JavascriptCore & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042}}
    & 2 & HI & \jerry{}\\
    12 & 7/10 & quickfuzz & \jsc{} & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187520}{\#187520}}
    & 2 & HI & \jerry{}\\
    13 & 7/10 & quickfuzz & \chakra{} & \textbf{Confirmed}  &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5443}{\#5443}}
    & 2 & HI & \jerry{}\\
   \bottomrule
  \end{tabular}
\end{table*}

>>>>

\subsection{Clusterization}
\label{sec:clusterization}

@@

This section reports the results obtained with differential
testing. More precisely, we report results obtained by fuzzing test
inputs, running those inputs on different engines, and checking the
outcomes with a differential oracle (see Figure~\ref{fig:workflow}).

\subsubsection{Methodology}
The methodology we used to assess the effectiveness of cross-engine
differential testing is as follows. To avoid experimental noise, we
only fuzz test files that pass in all engines. The intuition is that
we wanted to avoid the scenario where fuzzing produces a
fault-revealing input based on a test that was already
fault-revealing. This decision ensures that we can establish
cause-effect relationship between fuzzing and the observation of
discrepancy. Column ``no-fail-in-all'' from
Table~\ref{tab:test-suites} shows that a total of
\totalTestFilesPassInAll\ tests satisfy this restriction.

\vspace{1ex}
\noindent\textbf{Exploratory Phase.} For the first four months of the
study, our inspection process was exploratory.  Our goal in this phase
was to learn the extent to which \lo\ warnings could reveal bugs. We
realized that if we found that the ratio of bugs from \lo\ warnings
was rather low, we could focus our inspection efforts only on
\hi\ warnings. That finding would be important to reduce inspection
cost and guide future developments of this approach. To run this
experiment, we trained eight students in analyzing the warnings that
our infrastructure produces. The students were enrolled in a
graduate-level testing class. We listed warnings in a spreadsheet and
requested students to update an ``owner'' column indicating who was
working on it, but we did not enforce an order on the warnings the
students should inspect. Recall from Section~\ref{sec:clusterization}
that we clustered \lo\ warnings in buckets. For that reason, we only
listed one \lo\ warning per representative class/bucket in the
spreadsheet. First, we explained the possible sources of false alarms
with examples and then we asked the students to use the following
procedure when finding a suspicious warning. Analyze the parts of the
spec related to the problem and, if still suspicious, look for
potential duplicates on the bug tracker of the affected engine using
related keywords. If none was reported, indicate in the spreadsheet
that that warning is potentially fault-revealing. We encouraged
students to use lithium~\cite{lithium} to minimize long test cases;
the tests from the Mozilla suite are often longer than others. Only
after the co-authors checked the potential bugs, a bug report was
filed.

\vspace{1ex}
\noindent\textbf{Non-Exploratory Phase.} Results obtained in the
exploratory phase confirmed our expectations that most of the bugs
found during the initial four months of investigation were related to
\hi\ warnings. For that reason, we changed our inspection
strategy. This time, only the co-authors inspected the bugs using a
similar discipline as before. However, the set of warnings inspected
and the order of inspection changed. We restricted our analysis to
\hi\ warnings and, aware that we would be unable to analyze each and
every warning reported, we grouped those warnings per engine,
analyzing each group in a round-robin fashion. The rationale was to
give attention to each engine more uniformly, enabling more fair
comparison across engines. We repeated the following routine until
Aug. 22, 2018. We sampled five warnings associated with the group of a
given engine, analyzed these warnings, and moved to the group of
warnings associated with the next engine.

@@

\begin{table*}[h!]
  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued as result of cross-engine
    differential testing.}
  \label{tab:bugs}
  \begin{tabular}{ccccccccc}
    \toprule
    Issue\#    & Date & Fuzz & Engine  & Status  &
    \multicolumn{1}{c}{Url}  & Severity & Priority & Suite \\
    \midrule
    \multicolumn{9}{c}{\emph{Exploratory Phase}} \\
    \midrule    
    1  & 4/12 & radamsa & \chakra{}   & \textbf{Fixed}  &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/4978}{\#4978}}
    & 2 & LO & \jsc{} \\ 
    2  & 4/12 & radamsa & \chakra{}   & Rejected  &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/4979}{\#4979}}
    & - & HI & \jsc{} \\
    3  & 4/14 & radamsa & JavascriptCore  & New &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}
    } & -  & HI & \jsc{}    \\
    4  & 4/25 & radamsa & \chakra{}  & \textbf{Fixed}     &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5038}{\#5038}}
    & 2 & HI & \jerry{}   \\
    5  & 4/29 & radamsa & JavascriptCore  & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}
    } & 2  & HI  & \jerry{}\\
    \midrule
    \multirow{2}{*}{6} & \multirow{2}{*}{4/30}  &
    \multirow{2}{*}{radamsa} & \chakra{} & \textbf{Confirmed} &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5076}{\#5076}}
    & 2 & \multirow{2}{*}{HI} & \multirow{2}{*}{TinyJS}\\    
                        &                        &        &
    JavascriptCore & New &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}}
    & - &  & \\
    \midrule
    7 & 5/02 & radamsa & JavascriptCore  & \textbf{Fixed} &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}}
    & 2 & LO & \smonkey{} \\
    8 & 5/10 & radamsa & \chakra{} & \textbf{Confirmed} &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5128}{\#5128}}
    & 3 & HI & \jerry{} \\
    9 & 5/17 & radamsa & \chakra{} & \textbf{Fixed} &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5182}{\#5182}}
    & 2 & HI & \veight{}\\
    10 & 5/24 & radamsa & JavascriptCore & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943}}
    & 2 & HI & \jsc{}\\
    11 & 6/26 & radamsa & JavascriptCore & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042}}
    & 2 & HI & \jerry{}\\
    12 & 7/10 & quickfuzz & \jsc{} & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187520}{\#187520}}
    & 2 & HI & \jerry{}\\
    13 & 7/10 & quickfuzz & \chakra{} & \textbf{Confirmed}  &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5443}{\#5443}}
    & 2 & HI & \jerry{}\\
    \midrule        
    \multicolumn{9}{c}{\emph{Non-Exploratory Phase}} \\
    \midrule    
   \bottomrule
  \end{tabular}
\end{table*}
